Supporting Information\\ \textit{Cross Validation Approaches for Penalized Cox Regression}

### 2022-10-27 sub/smimr/response.tex

\documentclass[12]{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin = 1in]{geometry}
\usepackage{enumitem}
\usepackage{color}
\usepackage{amssymb,amsmath}

\newcommand{\re}{\textbf{Response: }}
\newcommand\pb[1]{{\color{red}#1}}
\newcommand\bd[1]{{\color{blue}#1}}
\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\boldeta}{\boldsymbol\eta}

\begin{document}

\subsubsection*{Response to comments by Reviewer \#1}

Thank you very much for your careful reading of the paper and your insightful comments, particularly regarding issues relating to time-varying covariates. You raise a number of good points and we have modified the manuscript considerably based upon your feedback.  In our opinion, these revisions have very much improved upon the original submission.

@@

\begin{enumerate}[align = left]
\item On p.4, roughly line 34, you have the statement “although the methods we analyze can be used with any penalty”.  This statement should be further elaborated, providing some tangible examples (including beyond the straightforward elastic net approach considered in the application analysis).

\re Thank you for this comment. In the revision (page 4), we provide a few examples of penalty functions, such as the elastic net penalty, smoothly clipped absolute deviations (SCAD) penalty, and minimax concave penalty (MCP). We also mention this in the Discussion section.

\item Though you aim to make various considerations in your simulation study, the impact of this work may very well be limited given consideration of only exponential survival distribution and independent censoring. Even common choices for a more complex distributional form, such as Weibull and Gompertz, might be considered too limiting. See, for example, Harden and Kropko (2019).

\textbf{Response (distributional form):} You raise a good point -- we did not expect the results to change much depending on the distributional form, but this is something that deserves to be investigated. In the revised supplementary material, we include additional simulation results where the baseline hazard is generated from Weibull and Gompertz distributions. The overall conclusions remain fairly similar, however. This is mentioned in the revised manuscript in the text surrounding Table 1.

\textbf{Response (independent censoring):} With regard to independent censoring, however, we feel that this would muddy the waters regarding whether a cross-validation method is working well or not. If the assumptions of the Cox model are not met, the partial likelihood is incorrect, and all models are wrong, which model should you choose? For example, suppose model A predicts well, but the coefficient estimates are biased, whereas model B estimates the coefficients more accurately but is worse at predicting the outcome. Is a cross-validation that favors model B better or worse than one that favors model A? These questions are interesting, but they have no clear answer and don't offer much help in terms of objectively determining which CV approach is best. See also point \ref{limitations} below.

\item Extensions into time-varying covariates, and, preferably, joint modeling, would be useful as well. At least the first two items (more flexible survival distributions, and dependent censoring) should be explored in your work, while perhaps extensions into joint modeling to accommodate one or more longitudinal predictors could be discussed as future work in your Discussion.

\re This is an excellent point -- additional issues may certainly arise when applying cross-validation to time-varying data. Our experience with high-dimensional Cox regression has tended to involve features that were only measured once due to the cost of these experiments, but as this cost goes down, that may certainly change. We feel that addressing these issues is beyond the scope of the current manuscript, but is definitely something worth discussing. The final paragraph of our discussion now points out these issues and discusses that future work is necessary to investigate the application of the proposed approach to these settings. \pb{ADD THIS PARAGRAPH}

\item \label{limitations} Speaking of your Discussion section, there is no mention of any limitations of the current work. Aside from the joint modeling comment above, you should also talk about violations of linearity, and of non-proportional hazards. That is, you need to provide a number of additional sentences, and references, as warranted, to talk about how the current contributions could ultimately be made more generalizable to various survival dataset characteristics, and not just those with a very simplifying structure. Some discussion on how to think about survival datasets with rare events should be commented on as well.

@@

\item There are several typos sprinkled throughout the paper, so a careful proofreading is required. Some examples include: (i) Section 3.1, second paragraph, where the phrase “the value of $\beta$ used the generate the data” requires editing. (ii) Table 1, Scenario 4, would seem to be for
strong signal, not weak. (iii) p.22, “more clear” should be changed to “clearer”.

\re Thank you for catching those. We made edits in the manuscript.

\end{enumerate}

\newpage

\subsubsection*{Response to comments by Reviewer \#2}

### 2022-10-27 main.tex
Edits to responses

In this paper, we focus upon the LASSO penalty $P_{\lambda}(\bbeta) = \lambda \sum_{j} |\beta_{j}|$, although the methods that we analyze not only can be used for penalized Cox regression with any penalty, such as elastic net \citep{Zou2005}, smoothly clipped absolute deviations (SCAD) penalty \citep{FanLi2001}, and minimax concave penalty (MCP) \citep{Zhang2010}, but are also applicable to model selection in unpenalized Cox regression. LASSO-penalized Cox regression is particularly useful for high dimensional data where the number of covariates $p > n$, such as predicting overall survival in cancer patients based on genome-wide expression measurements. LASSO estimates yield a sparse model where some coefficients are exactly zero. This sparsity pattern changes as we vary $\lam$: at large values of $\lambda$, most or all of the coefficients are 0, but as $\lam$ decreases, more covariates are selected. Selecting $\lambda$ is critical to LASSO estimation in the sense that the model's accuracy suffers if $\lam$ is either too large or too small.

>>>>

In this paper, we focus upon the LASSO penalty $P_{\lambda}(\bbeta) = \lambda \sum_{j} |\beta_{j}|$ as it is most common, although the need to select regularization parameters arises in all penalized regression models, such as elastic net \citep{Zou2005}, smoothly clipped absolute deviations (SCAD) penalty \citep{FanLi2001}, and minimax concave penalty (MCP) \citep{Zhang2010}. Indeed, cross-validation can be used for model selection in Cox regression even without the presence of a penalty, so the relevance of this question is wide-ranging. LASSO-penalized Cox regression is particularly useful for high dimensional data where the number of covariates $p > n$, such as predicting overall survival in cancer patients based on genome-wide expression measurements. LASSO estimates yield a sparse model where some coefficients are exactly zero. This sparsity pattern changes as we vary $\lam$: at large values of $\lambda$, most or all of the coefficients are 0, but as $\lam$ decreases, more covariates are selected. Selecting $\lambda$ is critical to LASSO estimation in the sense that the model's accuracy suffers if $\lam$ is either too large or too small.
